Title Goes Here

### 2020-05-01 analysis/paper/paper.Rmd
STM

>>>>

We then tried another process of topic modeling called Structural Topic Model (STM) which is very similar to the LDA we have described above. The main advantage for us is that, the STM allows us to include, alongside the normal topic modeling process, other metadata. This process "attaches" the metadata to the collection of texts that we will then perform topic modeling process. It is important to note that we have used the stm package that also includes the ability to calculate the number of topics that is best suited for STM modeling (Roberts 2019). The fact that we are allowed to do this allows us to perform covariate analysis (Roberts et al. 2013). This basically means that we can examine the relationship between the topics and some covariates/variables of interest. We can define the genders of males and females and then analyze the prevelance of these two categories in accordance with the topics that the stm package determined (Roberts 2019). The analysis is used also with probabilities given to the texts to see if the most occuring of some text seems to be "attached" to one gender over another.
